ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
Changes to bib

The environment and the object placement within it for both experiments was modelled on a typical office.
Measures were taken to ensure that both office environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
The objects in the guided experiment environment are

>>>>

The environment and the object placement within it for both experiments was modelled on a typical office.
Measures were taken to ensure that both office environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, which is not a problem since most offices contain the same basic furniture and objects. 
These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
The objects in the guided experiment environment are
